Topology, geometry and morphology of the dark matter web

### 2018-06-18 Draft/thesis-ku.tex
proof-reading

% Set the title and author info
\title{Dark matter web in the Universe}
\author{Nesar Ramachandra}

@@

>>>>

% Set the title and author info
\title{Topology, geometry and morphology of the dark matter web}
\author{Nesar Ramachandra}

@@

% 2018 Paper

Recent developments in numerical analysis of cosmological simulations have hinted towards dynamical information of gravitational clustering. This is inferred from a six-dimensional Lagrangian sub-manifold – comprising of initial and final co-ordinates of dark matter particles. Velocity multi-stream fields that are derived from this sub-manifold have shed new light on the nature of Dark matter Universe.

Structures in the Dark matter Universe
As a part of my doctoral dissertation under Professor Sergei Shandarin, I work on problems regarding Dark Matter clustering in the Universe. Recent developments in numerical analysis of cosmological simulations have hinted towards dynamical information of gravitational clustering. This is inferred from a six-dimensional Lagrangian sub-manifold – comprising of initial and final co-ordinates of dark matter particles. Velocity multi-stream fields that are derived from this sub-manifold have shed new light on the nature of Dark matter Universe. One such high-resolution analysis of dark matter halo (most dense regions in the Dark Matter Universe) environments run on the cluster computation facilities at the Center for Research Computing, University of Kansas is shown below:

We have extended our work to topological and geometrical descriptions of the cosmic web. Percolation studies on cosmic fields display a transitions in connectivities of structures, and Hessian analysis delineates structures with different shapes – tubular, sheet-like, or globular. Our recent paper claims that the over 99 per cent of the voids are connected. Another geometrical analyses has paved the way for detection of haloes in numerical simulations. We have developed a halo-finder algorithm based on the compact geometries of the halo surfaces and the number of gravitational collapses undergone by dark matter particles.

The large scale Distribution of dark matter follows

Galaxies play a role of lights illuminating these structures so they can be observed. The observations in the last several decades have unveiled rich geometry of these structures currently known as the cosmic web.

Gravitational evolution of
